The very dependent recursive structure of iterated parametricity in indexed form

### 2025-12-29 paper/paper.tex
paper: minor tweaks; simplification effort in progress

Also, when $n$ is 0, we write $E$ to denote an element $(\unitpoint, E)$ of $\fulldepstype[0]$.

@@

By abuse of notation, we also write $E$ for an inhabitant of $\depscohstype[n]$ (standing for a non trivial inhabitant of $\fulldeps[n]$).

@@

\begin{equation*}
  \begin{array}{lcl}
    \overline{\fulldepscohs}(\fulldepscoht[n]) & :      & \fulldepscohstype[n+1]                                        \\
    \overline{\fulldepscohs}(\fulldepscoht[n]) & \defeq & \left(\begin{array}{l}
                                                                    \overline{\depscohs}(\depscoht[n][\lbrack 0,n \rbrack]) \\
                                                                    E                                                       \\
                                                                  \end{array}\right) \\
  \end{array}
\end{equation*}

>>>>

Also, when $n$ is $0$, we write $E$ to denote an element of $\fulldepstype[0]$ where all other components are degenerate.

@@

@@

\begin{equation*}
  \begin{array}{lcl}
    \overline{\fulldepscohs}(\fulldepscoht[n]) & :      & \fulldepscohstype[n+1] \\
    \overline{\fulldepscohs}(\fulldepscoht[n]) & \defeq & \left(
    \begin{array}{l}
        \overline{\depscohs}(\depscoht[n][\lbrack 0,n \rbrack]) \\
        E                                                       \\
      \end{array}\right)                      \\
  \end{array}
\end{equation*}
